Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-11 eswc-2012/phdsymp.tex
gc may be random
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@59 43ef1190-90fd-4dd7-a769-d0121f02b80e

When the difference is little, we must consider the possibility that
the measurements are impacted by random noise. Computer systems are
generally very deterministic systems, but there are nevertheless many
such scenarios: The underlying system may be doing other tasks. This
is likely to be particularly important in enterprise environments
where high-load applications are often running on virtual
machines. The engine may use randomized algorithms, or the data may be
of such a nature it triggers worst-case behaviour in situations the
query writer cannot foresee. All this contributes to that we should
consider the performance metric, whatever metric is used, as a
\emph{stochastic variable}.

>>>>

When the difference is little, we must consider the possibility that
the measurements are impacted by random noise. Computer systems are
generally very deterministic systems, but there are nevertheless many
such scenarios: The underlying system may be doing other tasks. This
is likely to be particularly important in enterprise environments
where high-load applications are often running on virtual
machines. The garbage collection of some languages may trigger on not
easily foreseeable points. The engine may use randomized algorithms,
or the data may be of such a nature it triggers worst-case behaviour
in situations the query writer cannot foresee. All this contributes to
that we should consider the performance metric, whatever metric is
used, as a \emph{stochastic variable}.
